Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2022-09-20 ba_resubmit/response_to_reviewers.tex

	The paper presents a computational variant of the method introduced by Sadinle (2017). Simulation results are presented and the variant is applied on a new, significantly larger data set. A significant part of the paper is a reproduction of the paper of Sadinle. The variant is introduced in section 4. It is simple but consequential. The simulations and applications show how the variant accelerates the computation relative to the original method and reveals the trade-offs.

	The value of the paper resides in that computational complexity continues to be a difficult obstacle in the application of Bayesian statistics. The proposals of the paper enable the application of Sadinle’s approach to an extent not possible before. It is important to present the research for what it is: An extension of the method of Sadinle motivated by computational considerations. Here Sadinle supersedes Fellegi-Sunter in the sense while the starting point of Sadinle’s research is Fellegi-sunter, the starting point of this paper is Sadinle’s work. This should be made clearer, beginning in the abstract and reiterated in the conclusion.

	\reply{%
		\textcolor{red}{BEKA/JERRY: I think this reviewer wants us to explicitly mention Sadinle in the abstract. I think I had that originally, but we removed it. Please advise on the best way to address this comment.}
	}

\section{Additional Points Addressed}

We highlight some additional points addressed in our revision. \todo
\textcolor{blue}{Brian: These are just some suggestions that I have, so we can chat through these in case you don't agree! I have these marked up on the paper itself to help you more easily make the changes.}

\begin{enumerate}
\item We have added introductory sentences to each section/subsection to provide more guidance to the reader. 
\item The word databases is used throughout instead of files or lists. 
\item We have checked for the proper use of commas throughout the paper. 
\item We have re-written our proposed work on page 2 to make it more clear our contributions to the literature as it was missing our improvements over existing work in terms of speed with minimal loss in accuracy as well as providing two case studies. One case study is from the original paper of our extension, while another case study illustrates our ability to scale to larger databases. We provide a more comprehensive discussion regarding our work. 
\item We have broken up sentences that are too long.
\item We have removed repetitive words, such as intuitive, additionally.  \textcolor{blue}{Brian: you can use something like antidote to check for these or go through yourself. Be careful with the word intuitive. While it might be obvious to you, it may not be obvious to the Editor and this word can be quite jarring). As an example, in my job talk, Mike West did not find the linkage structure to be intuitive and found it to be quite weird and confusing!}
\item We have checked that we define terms before they are introduced. 
\item We have defined the parameters $m$ and $u$ on page 4. 
\item One page 5, section 2.2, we have made it more clear why our extension is warranted and needed in the literature. 
\item We have removed confusing language, such as "compactful representation of" on page 5. 
\item We have checked that fast beta linkage is represented by fabl throughout. 
\item \textcolor{blue}{See page 10 for a long list of comments.}
\item We do not start sentences with a Greek letter or a parameter.
\item We have fixed the sentence ``sampling a value from...." that has a missing verb (see page 11).
\item We have fixed a typo in equation 6, which is a missing (). 
\end{enumerate}
\end{document}

### 2022-09-20 ba_resubmit/kundinger_resubmit.tex
proposed change on p11.

	We emphasize the computational gains of this split sampler: the first step is a sample from $P$ options, where $P$ does not scale with the size of the linkage task; and the second step is sampling uniformly at random, which is computationally simple even for large sets of candidate records. These changes drastically improve the speed of the sampler, and each can be parallelized if desired for additional computational gains. We provide a summary of the \texttt{fabl} method through psuedocode in Appendix \ref{app:fabl-psuedocode}. We note here that this split sampler can be adapted for use with \texttt{BRL} as well, but would require updating $\{H_j\}$ to account for the previously matched records that no are longer candidate matches for the current record. \texttt{BRL} would see considerable speed up through the procedure, but computation time would still scale with the size of the larger dataset.

%	\hypertarget{computational-complexity}{%
%		\subsection{Computational Complexity}\label{computational-complexity}}
	We close this section by proving the computational complexity of \texttt{fabl}.

>>>>

	We emphasize the computational gains of this split sampler: the first step is a sample from $P$ options, where $P$ does not scale with the size of the linkage task; and the second step is sampling uniformly at random, which is computationally simple even for large sets of candidate records. These changes drastically improve the speed of the sampler, and each can be parallelized if desired for additional computational gains. We provide a summary of the \texttt{fabl} method through psuedocode in Appendix \ref{app:fabl-psuedocode}. \textcolor{blue}{The computational complexity of \texttt{fabl} is given in Lemma \ref{lemma:fabl}.}

%	We close this section by proving the computational complexity of \texttt{fabl}.

	\begin{remark}
	We note here that this split sampler can be adapted for use with \texttt{BRL} as well, but would require updating $\{H_j\}$ to account for the previously matched records that no are longer candidate matches for the current record. \texttt{BRL} would see considerable speed up through the procedure, but computation time would still scale with the size of the larger dataset.
	\end{remark}

%	\hypertarget{computational-complexity}{%
%		\subsection{Computational Complexity}\label{computational-complexity}}
